---
title: "Analysis"
author: "Aashna"
format: html
execute: 
  echo: false
---

```{r}
 #| message: FALSE 
library(tidyverse)
library(primer.data)
library(tidybayes)
library(brms)
library(gtsummary)
```

```{r}
nhanes |> 
  filter(sex == "Male", age >= 18) |> 
  select(height) |> 
  drop_na() |>  
  ggplot(aes(x = height)) + 
    geom_histogram(bins = 50) +
    labs(title = "Male Adult Height in the US in 2010", 
    y = "Count", x = "Height (cm)", 
    caption = "Source: National Health and Nutrition Examination Survey")
```

```{r}
#| cache: TRUE
fit_male_height <- brm(formula = height ~ 1, data = ch5, 
family = gaussian(), silent = 2, 
refresh = 0,  seed = 12)
```

```{r}
tbl_regression(fit_male_height, intercept = TRUE)

```

```{r}
#| label: plot
ndata <- tibble(.rows = 1)
fit_male_height |> 
add_predicted_draws(newdata = ndata) |> 
ggplot(aes(x = .prediction)) +
geom_histogram(aes(y = after_stat(count / sum(count))),
bins = 100) + labs(title = "Posterior for Height of Random Male", 
subtitle = "Uncertainty for a single individual is much greater than for the expected value", 
y = "Probability", x = "Height (cm)", 
caption = "Data source: NHANES") + 
scale_x_continuous(labels = scales::number_format()) + 
scale_y_continuous(labels = scales::percent_format(accuracy = 1))
```

```{r}
fit_male_height |> 
  add_predicted_draws(newdata = ndata) |> 
  mutate(tall = if_else(.prediction > 180, TRUE, FALSE)) |> 
  summarize(odds = mean(tall))
```

In data science, wisdom involves understanding the problem, selecting appropriate methods, and effectively communicating findings. Using a Bayesian linear regression model in this analysis, I'm exploring male adult height trends based on data from the National Health and Nutrition Examination Survey (NHANES), aiming to provide insights into height distribution and potential influencing factors. We can use the graphs to estimate the answer for our question.




